\section*{General Outline and Motvations Driving Data Processing \& Analysis}
We are already ensuring open access to representative data sets, processeing pipelines and analysis tools in 
support of the preparation of both Cycle 1 and Cycle 2 proposals. 
%engage a broad cross-section of the astronomical community in familiarizing themselves with JWST data and scientific capabilities.
The key links are:: \\ 

%\vspace{6pt}
%\noindent
%\vspace{4pt}
\href{https://github.com/d80b2t/JWST\_ERS}{{\tt github.com/d80b2t/JWST\_ERS}} 

(the P.I.'s personal and public GitHub repository).
\\

%\vspace{6pt} 
%\noindent
\href{https://github.com/miri-mrs}{{\tt github.com/miri-mrs}} 

(a ``Organizational'' public GitHub repository for the Community).
\\

%\vspace{6pt}
%\noindent
\href{http://miri-mrs.readthedocs.io/en/latest/}{{\tt miri-mrs.readthedocs.io}}

(With the source code here: \href{https://github.com/miri-mrs/ERQs/tree/master/docs}{{\tt https://github.com/miri-mrs/ERQs/tree/master/docs}}). \\


\medskip \medskip
\noindent
Our ERQ ERS proposal is the first part of a multi-cycle proposal
project and plan.  As such, we are {\it already highly motivated to
produce the data processing tools, codes, documentation and identify
the critical science-enabling products well in advance of the release
of the Cycle 2 Call for Proposals (September 2019).}

\smallskip \smallskip
\noindent
Our Science-Enabling Products team consists of five main parts::
\begin{itemize}
    \item ``Core Coders''; 
    \item Website and \href{http://miri-mrs.readthedocs.io/en/latest/}{{\tt ReadTheDocs}} Writers; 
    \item Observational Follow-up; 
    \item Senior members of staff, able to supply students/ ask for funding; 
    \item A small steering committee. 
\end{itemize}


\section*{ERS ERQ Science Enabling Products}
{\tt mrs\_analyzer} is  a Python module for analyzing MRS data; \\
{\tt mrsfringe} is a Python module for mitigating MRS fringing issues; \

\smallskip \smallskip
\noindent
And will integrate with...\\
\href{https://github.com/STScI-JWST}{\tt https://github.com/STScI-JWST} \\
see e.g. \\
{\tt https://github.com/STScI-JWST/jwst/blob/master/jwst/mrs\_imatch/mrs\_imatch\_step.py}\\


\section*{MIRISim}
MIRI data simulations (at ESA) include an Integral Field observation
with the Medium Resolution Spectrograph (MRS), a Low Resolution
Spectrograph (LRS) observation, and an imaging observation. (Credit:
ESA, Pamela Klaassen and the MIRISim Team).

\iffalse
\section{Useful links}
http://astroconda.readthedocs.io/en/latest/ \\
https://www.cosmos.esa.int/web/jwst/simulations\\
https://confluence.stsci.edu/display/JWSTDADF/JWST+Data+Analysis+Development+Forum\\
https://jwst.stsci.edu/science-planning/data-analysis-toolbox\\
https://www.youtube.com/watch?v=A024z9CITZs\\
https://jwst.stsci.edu/science-planning/proposal-planning-toolbox/simulated-data\\
\fi


\section*{Delivery Schedule for Science-Enabling Products.} 
Proposals must present a delivery schedule for science-enabling products. A description of STScI pipeline data products, processing and analysis software, and their anticipated availability, will be provided by the May 2017 release of the final version of this Call for Proposals.  Proposers may consider multiple deliveries, with more advanced products provided over longer timescales. Proposals may include the collection, processing and analysis of ancillary data as part of an integrated DD ERS proposal.


\section*{Co-Investigators and Delivery of Science-Enabling Products.}
Co-Investigators, together with the PI (and any Co-PIs) comprise a core team with the responsibility of developing and delivering science-enabling products as described in the proposal, as well as carrying out selected key aspects of the science investigations.  A Co-I must have a well-defined, and generally sustained, continuing role in team activities, serve under the direction of the PI, or co-PI(s). Co-investigators may or may not receiving funding, pending eligibility, through the DD ERS program. A bibliography and SEP tasks of our team can be found \href{https://github.com/d80b2t/JWST_ERS/blob/master/Proposal/CoI_bios.tex}{here} and the SEP Deliverables are \href{https://github.com/d80b2t/JWST_ERS/tree/master/Deliverables}{here}. 

%\input{CoI_bios.tex}



