
\subsection{Dr. Nicholas Ross}
P.I. Dr. Nic Ross is a deep believer in delivering science-enabling
products, including datasets, catalogs, analysis codes, plots,
algorithms and where possible computational resources to the wide
astronomical community.  As such, the call for delivering
science-enabling products by the release of the Cycle 2 Call for
Proposals (September 2019) is fully inline with his scientific
practice.

Ross has being developing and buidling up his GitHub Repositories over
the last year or so, \href{https://github.com/d80b2t}{\tt
github.com/d80b2t} and indeed now does all his analysis and paper
writing on GitHub.

Ross will devote a considerable amount of his personal research time
(and due to his STFC ERF has 100\% FTE for research) to leading the
developement and timely prodcution of the ERS ERQ science-enabling
products.


\subsection{Dr. David Rosario} 
Co-PI Dr. David Rosario is awesome and loves also writing code. 


\subsection{Prof. David Alexander} 
Prof. Alexander is an expert in high-$z$ obsured AGN.  He will use his
considerable {\it Spitzer IRS} expereince to help test our MIRI MRS
data-analysis toolkit.


\subsection{Dr. Rachael Alexandroff} 
Dr. Alexandroff is an leading expert on the ERQ population. 
She will bring to bear her now considerable and recent data analysis 
(long-slit optical, polarimerty, radio) data analysis experience to 
build our MIRI MRS data-analysis toolkit.


\subsection{Dr. Richard Bielby}


\subsection{Prof. Beth Biller}


\subsection{Prof. Niel Brandt}


\subsection{Dr. Rob Crain}


\subsection{Prof. Xiaohui Fan}


\subsection{Prof. Fred Hamann}


\subsection{Prof. Dale Kocevski}


\subsection{Prof. Linhua Jiang}


\subsection{Dr. Stephanie LaMassa}


\subsection{Dr. Chelsea MacLeod}


\subsection{Dr. Ian McGreer}


\subsection{Prof. Brice Menard}	


\subsection{Dr. James Mullaney}


\subsection{Prof. Adam Myers}


\subsection{Dr. Jessie Runnoe}


\subsection{Prof. Don Schneider}


\subsection{Prof. Tom Shanks}	


\subsection{Dr. John Stott}


\subsection{Prof. Michael  Strauss}


\subsection{Dr. Renske Smit}		


\subsection{Prof. Martin Ward}		


\subsection{Prof. Gillian Wright}


\subsection{Prof. Nadia Zakamsaka} 